A Linear Solution of the Linearity Challenge

### 2025-12-16 paper/related.tex
notes for table

\begin{table}[t]
    \newcommand{\textlabel}[1]{\rotatebox{90}{#1}}
    \newcommand{\CHECK}{\checkmark}
    \newcommand{\SessionPI}{session $\pi$}
    \newcommand{\SessionLAM}{session $\lambda$}
    \caption{\label{tab:comparison} Comparison of different formalizations of binary session calculi.}
    \begin{tabular}{@{}r|c|ccc|rr|rr|r@{}}
        \textbf{Formalization} &
        \textlabel{Proof assistant} &
        \textlabel{Calculus} &
        \textlabel{Shared channels} &
        \textlabel{Polymorphism} &
        \textlabel{Subject reduction} &
        \textlabel{Library} &
        \textlabel{Deadlock freedom} &
        \textlabel{Library} &
        \textlabel{\bf Total size}
        \\
        \hline
        \fullcite{GotoEtAl16} &
        Coq &
        \SessionPI & 
        \CHECK &
        \CHECK &
        543 &
        -- &
        -- &
        -- &
        \textbf{563}
        \\
        \fullcite{Thiemann19} &
        Agda &
        \SessionLAM &
        \CHECK &
        -- &
        177 &
        -- &
        -- &
        -- &
        \textbf{177}
        \\
        \fullcite{CastroFerreiraYoshida20} &
        Coq &
        \SessionPI &
        \CHECK &
        -- &
        204 &
        -- &
        -- &
        -- &
        \textbf{204}
        \\
        \fullcite{CicconePadovani20} &
        Agda &
        linear $\pi$ & 
        \CHECK &
        -- &
        77 &
        -- &
        -- &
        -- &
        \textbf{77}
        \\
        \fullcite{RouvoetPoulsenKrebbersVisser20} &
        Agda &
        \CP &
        -- &
        -- &
        27 &
        55 &
        -- &
        -- &
        \textbf{82}
        \\
        \fullcite{ZalakainDardha21} &
        Agda &
        graded $\pi$ &
        \CHECK &
        -- &
        82 &
        8 &
        -- &
        -- &
        \textbf{90}
        \\
        \fullcite{JacobsBalzerKrebbers22} &
        Coq &
        \SessionLAM &
        -- &
        -- &
        68 &
        -- &
        25 &
        171 &
        \textbf{264}
        \\
        \fullcite{SanoKavanaghPientka23} &
        Beluga &
        S\CP &
        -- &
        -- &
        35 &
        -- &
        -- &
        -- &
        \textbf{35}
        \\
        \fullcite{ZackonEtAl25} &
        Beluga &
        \CP &
        -- &
        -- &
        56 &
        73 &
        -- &
        -- &
        \textbf{129}
        \\
        this work &
        Agda &
        linear \CP &
        \CHECK &
        \CHECK &
        21 &
        -- &
        15 &
        -- &
        \textbf{36}
    \end{tabular}
\end{table}

>>>>

\begin{table}[t]
    \newcommand{\textlabel}[1]{\rotatebox{90}{#1}}
    \newcommand{\CHECK}{\checkmark}
    \newcommand{\SessionPI}{session $\pi$}
    \newcommand{\SessionLAM}{session $\lambda$}
    \caption{\label{tab:comparison} Comparison of different formalizations of binary session calculi.}
    \begin{minipage}{.9\textwidth}
    \begin{tabular}{@{}r|c|ccc|rr|rr|r@{~}l@{}}
        \textbf{Formalization} &
        \textlabel{Proof assistant} &
        \textlabel{Calculus} &
        \textlabel{Shared channels} &
        \textlabel{Polymorphism} &
        \textlabel{Subject reduction} &
        \textlabel{Library} &
        \textlabel{Deadlock freedom} &
        \textlabel{Library} &
        \textlabel{\bf Total size} &
        \\
        \hline
        \fullcite{GotoEtAl16} &
        Coq &
        \SessionPI & 
        \CHECK &
        \CHECK &
        543 &
        -- &
        -- &
        -- &
        \textbf{563} &
        \footnote{Excluding safety results.}
        \\
        \fullcite{Thiemann19} &
        Agda &
        \SessionLAM &
        \CHECK &
        -- &
        177 &
        -- &
        -- &
        -- &
        \textbf{177} &
        \footnote{Including support for subtyping and the interpreter.}
        \\
        \fullcite{CastroFerreiraYoshida20} &
        Coq &
        \SessionPI &
        \CHECK &
        -- &
        204 &
        -- &
        -- &
        -- &
        \textbf{204} &
        \footnote{Excluding the original syntax.}
        \\
        \fullcite{CicconePadovani20} &
        Agda &
        linear $\pi$ & 
        \CHECK &
        -- &
        77 &
        -- &
        -- &
        -- &
        \textbf{77} &
        \footnote{Including support for dependent session types.}
        \\
        \fullcite{RouvoetPoulsenKrebbersVisser20} &
        Agda &
        \CP &
        -- &
        -- &
        27 &
        55 &
        -- &
        -- &
        \textbf{82} &
        \footnote{Including type-preserving evaluator and library for proof-relevant separation algebra.}
        \\
        \fullcite{ZalakainDardha21} &
        Agda &
        graded $\pi$ &
        \CHECK &
        -- &
        82 &
        8 &
        -- &
        -- &
        \textbf{90} &
        \footnote{Including library for algebra of types.}
        \\
        \fullcite{JacobsBalzerKrebbers22} &
        Coq &
        \SessionLAM &
        -- &
        -- &
        68 &
        -- &
        25 &
        171 &
        \textbf{264} &
        \footnote{Including deadlock freedom and the library for connectivity graphs.}
        \\
        \fullcite{SanoKavanaghPientka23} &
        Beluga &
        S\CP &
        -- &
        -- &
        35 &
        -- &
        -- &
        -- &
        \textbf{35}
        \\
        \fullcite{ZackonEtAl25} &
        Beluga &
        \CP &
        -- &
        -- &
        56 &
        73 &
        -- &
        -- &
        \textbf{129} &
        \footnote{Excluding the correspondence between \CP and S\CP.}
        \\
        this work &
        Agda &
        linear \CP &
        \CHECK &
        \CHECK &
        21 &
        -- &
        15 &
        -- &
        \textbf{36} &
        \footnote{Including deadlock freedom and excluding safety results.}
    \end{tabular}
    \end{minipage}
\end{table}
